---
title: "fars: datasets and functions about certain car accidents"
author: "IdleImpala"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{"fars: datasets and functions about certain car accidents"}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE,comment = "#>",echo=TRUE, eval=FALSE)
```

##Introduction

##Using the package

Let's import an example dataset from the package

```{r}
data(accident_2013)
```

The main functions within the package require a certain data title format. This is provided by the `make_filename()7 function.

```{r}
make_filename(2013)
```

Let's export export our dataset with the appropriate title format

```{r}
write.csv(accident_2013, make_filename(2013),row.names=FALSE)
```

Let's produce a summary of the year 2013.

```{r}
fars_summarize_years(2013)
```

It would be nice to see these accidents on a map. Let's print it for one of the states.

```{r}
fars_map_state(6,2013)
```

